\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{charter}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true,urlcolor=black}
\setlength{\parskip}{0.6em}
\setlength{\parindent}{0pt}

\begin{document}

% Header
\textbf{Yihang Huang}\\
Montreal, QC, Canada \\ 
\href{mailto:yihang.h16@gmail.com}{yihang.h16@gmail.com} \\ 
+1 514 746 9588 \\ 
\href{https://github.com/QuoiHang}{github.com/QuoiHang} \;|\; \href{https://linkedin.com/in/yihang-huang}{linkedin.com/in/yihang-huang}

\vspace{1.2em}
\today

\vspace{0.8em}
[Hiring Manager Name]\\
[Company Name]\\
[Team or Product Name]\\
[City, Province/State]

\vspace{0.8em}
\textbf{Re: Application for [Internship Title] – [Job ID]}

\vspace{0.6em}
Dear [Hiring Manager Name],

I am a Master of Computer Science student at the Université de Montréal (graduating 2026) seeking a [season/year] [Internship Title] at [Company Name]. I have been following your work on [briefly name a product/initiative], and I am excited about the opportunity to contribute and learn from your team.

\textbf{What I bring}
\begin{itemize}
  \item \textbf{Full-stack web experience.} At Arctic Star Foods, I administered and optimized PHP/MySQL web infrastructure (maintaining 99.9\% uptime), built a custom product-showcase web app, and integrated billing and order systems to streamline operations. Stack: PHP, MySQL, HTML/CSS/JavaScript, React, Docker.
  \item \textbf{Data/ML and product sense.} In my NHL Data Analyzer project, I collected and cleaned data from public APIs, trained models to forecast game outcomes and goal accuracy, and built a real-time web app for visualization. Tools: Python, pandas, scikit-learn.
  \item \textbf{Quality and automation mindset.} As a QA Engineer at Keywords Studios, I created automation tools in Python and VBA to reduce manual testing, partnered with studios like Warner Bros., Ubisoft, and 2K, and delivered feedback that improved user experience.
\end{itemize}

Across my coursework and projects, I am comfortable with C++, Python, Java, SQL, React, and Docker, and I value good engineering practices—version control, readable code, and pragmatic testing. I learn quickly, communicate clearly, and enjoy shipping features in collaborative environments.

I am available to start [Start Date] for [Duration] in [Location/Remote preference]. I would welcome the chance to discuss how my background can support [Team or Product Name] and [Company Name]'s goals. My resumé is attached, and code samples are available on GitHub.

Thank you for your time and consideration.

Sincerely,\\[6pt]
\textbf{Yihang Huang}\\
Montreal, QC \;|\; yihang.h16@gmail.com \;|\; +1 514 746 9588

\end{document}
